Re-run, Repeat, Reproduce, Reuse, Replicate:\\Transforming Code into Scientific Contributions

### 2017-08-23 draft.tex
Updated and simplified sources

print(walk)
with open("results-R2.txt", "w") as file: # Saving output to disk
    file.write(str(walk))
\end{code}
\end{minipage}\\

@@

\noindent \begin{minipage}[c]{\linewidth}
\begin{code}{\textbf{\textsc{Listing 4:}} Re-runnable, repeatable, reproducible random walk (R$^3$)}
# Copyright (c) 2017 Nicolas P. Rougier and Fabien C. Y. Benureau
# Release under the BSD 2-clause license
# Tested with CPython 3.6.1 / macOS 10.12.4 / 64 bits architecture
import platform, datetime
import random
import pip
import git

def git_info(): # Retrieve the code version
    repo = git.Repo(os.path.dirname(__file__), search_parent_directories=True)
    return {'hash': repo.head.object.hexsha, 'dirty': repo.is_dirty(),
            'git_version': str(pip.git.Git().get_git_version())}

def provenance(): # Get info about the execution environment
    return {'python'   : {'implementation': platform.python_implementation(),
                          'version'       : platform.python_version_tuple(),
                          'compiler'      : platform.python_compiler(),
                          'branch'        : platform.python_branch(),
                          'revision'      : platform.python_revision()},
            'platform' : platform.platform(),
            'packages'  : list(pip.commands.freeze.freeze()), # list of installed packages
            'git_info' : git_info(),
            'timestamp': datetime.datetime.utcnow().isoformat()+'Z'}  # Z stands for UTC

def walk():
    promenade, total = [], 0
    for i in range(10):
        step = +1 if random.uniform(-1,+1) > 0 else -1
        total += step
        promenade.append(total)
    return promenade

@@

# Random walk for 10 steps
seed = 1
random.seed(seed)
w = walk()

# Display & save results
print(w)
results = {'data': w, 'seed': seed, 'provenance': provenance()}
with open("results-R3.txt", "w") as fd:
    fd.write(str(results))
\end{code}
\end{minipage}\\

@@

\noindent \begin{minipage}[c]{\linewidth}
\begin{code}{\textbf{\textsc{Listing 5:}} Re-runnable, repeatable, reproducible, reusable random walk (R$^4$)}
# Copyright (c) 2017 Nicolas P. Rougier and Fabien C. Y. Benureau
# Release under the BSD 2-clause license
# Tested with CPython 3.6.1 / macOS 10.12.4 / 64 bits architecture
import platform, datetime, json
import random
import pip
import git

def git_info():
    """Retrieve the current git hash, and if the repository has uncommitted changes."""
    repo = git.Repo(os.path.dirname(__file__), search_parent_directories=True)
    return {'hash': repo.head.object.hexsha, 'dirty': repo.is_dirty(),
            'git_version': str(pip.git.Git().get_git_version())}

def provenance():
    """Get info about the execution environment and the code."""
    return {'python'   : {'implementation': platform.python_implementation(),
                          'version'       : platform.python_version_tuple(),
                          'compiler'      : platform.python_compiler(),
                          'branch'        : platform.python_branch(),
                          'revision'      : platform.python_revision()},
            'platform' : platform.platform(),
            'packages'  : list(pip.commands.freeze.freeze()), # list of installed packages
            'git_info' : git_info(),
            'timestamp': datetime.datetime.utcnow().isoformat()+'Z'}  # Z stands for UTC

def walk(n, seed):
    """Return a `n` steps random walk.
    `seed` is used to initialize the Mersene Twister random number generator."""
    random.seed(seed)
    rndwalk, total = [], 0
    for i in range(10):
        step = +1 if random.uniform(-1,+1) > 0 else -1
        total += step
        rndwalk.append(total)
    return rndwalk

def generate_results(n, seed, filename='results-R4'):
    """Generate results and save them to disk as a JSON file"""
    w = walk(n, seed)
    results = {'data': w, 'n': n, 'seed': seed, 'provenance': provenance()}
    with open(filename + '.json', 'w') as fd:
        json.dump(results, fd)
    return results

if __name__ == '__main__':
    # Unit test checking reproducibility
    assert walk(10, 1) == [-1, 0, 1, 0, -1, -2, -1, 0, -1, -2]

    print(generate_results(10, 1)['data'])
\end{code}
\end{minipage}\\

@@

def walk(rng, n):
    """Random walk for n steps."""
    # Note: We consider 0 to be a positive step
    steps = 2*(rng.uniform(-1,+1,n) > 0) - 1
    return steps.cumsum().tolist()

def rng(seed):
    """Return a random number generator initialized with seed."""
    rng = random.Random()
    rng.seed(seed)
    _, keys, _ = rng.getstate()
    rng = np.random.RandomState()
    state = rng.get_state()
    rng.set_state((state[0], keys[:-1], state[2], state[3], state[4]))
    return rng

if __name__ == '__main__':
    # Unit test
    assert walk(rng(seed=1), 10) == [-1, 0, 1, 0, -1, -2, -1, 0, -1, -2]

    # Random walk for 10 steps
    seed = 1
    x = walk(rng(seed=seed), 10)

    # Display & save results
    print(x)
    with open("results-R5-%d.txt" % seed, "w") as file:
        file.write(str(x))
\end{code}
\end{minipage}

>>>>

x =  0
path = []
for i in range(10):
    step = random.choice([-1,+1])
    x += step
    path.append(x)

print(path)
# Saving output to disk
with open("results-R2.txt", "w") as fd:
    fd.write(str(path))

\end{code}
\end{minipage}\\

@@

\noindent \begin{minipage}[c]{\linewidth}
\begin{code}{\textbf{\textsc{Listing 4:}} Re-runnable, repeatable, reproducible random walk (R$^3$)}
# Copyright (c) 2017 Nicolas P. Rougier and Fabien C. Y. Benureau
# Release under the BSD 2-clause license
# Tested with CPython 3.6.1 / macOS 10.12.4 / 64 bits architecture
import sys, subprocess, datetime, random

def walk():
    path = []
    x = 0
    for i in range(10):
        if random.uniform(-1,+1) > 0:
            x = x + 1
        else:
            x = x - 1
        path.append(x)
    return path

# If repository is dirty, don't run anything
if subprocess.call(("git", "diff-index", "--quiet", "HEAD")):
    print("Repository is dirty, please commit first")
    sys.exit(1)

# Get git hash if any
revision = subprocess.check_output(("git", "rev-parse", "HEAD"))

@@

# Random walk for 10 steps
seed = 1
random.seed(seed)
path = walk()

# Display & save results
print(path)
results = { 'data':      path,
            'seed':      seed,
            'timestamp': str(datetime.datetime.utcnow()),
            'revision':  revision,
            'system' :   sys.version }
with open("results-R3.txt", "w") as fd:
    fd.write(str(results))
\end{code}
\end{minipage}\\

@@

\noindent \begin{minipage}[c]{\linewidth}
\begin{code}{\textbf{\textsc{Listing 5:}} Re-runnable, repeatable, reproducible, reusable random walk (R$^4$)}
# Copyright (c) 2017 Nicolas P. Rougier and Fabien C. Y. Benureau
# Release under the BSD 2-clause license
# Tested with CPython 3.6.1 / macOS 10.12.4 / 64 bits architecture
import sys, subprocess, datetime, random

def walk(x0=0, step=1, count=10, seed=0):
    """ Random walk
        x0   : initial position (default 0)
        step : step size (default 1)
        count: number of steps (default 10)
        seed : seed for the initialization of the random generator (default 0)
    """
    path, x = [], x0
    random.seed(seed)
    for i in range(count):
        if random.uniform(-1,+1) > 0:
            x = x + step
        else:
            x = x - step
        path.append(x)
    return path

if __name__ == '__main__':
    # If repository is dirty, don't do anything
    if subprocess.call(("git", "diff-index", "--quiet", "HEAD")):
        print("Repository is dirty, please commit first")
        sys.exit(1)

    # Get git hash if any
    revision = subprocess.check_output(("git", "rev-parse", "HEAD"))

    # Unit test checking reproducibility
    assert walk(0, 1, 10, 1) == [-1, 0, 1, 0, -1, -2, -1, 0, -1, -2]

    # Simulation parameters
    parameters = { 'x0':    0,
                   'step':  1,
                   'count': 10,
                   'seed' : 1 }
    path = walk(**parameters)
    results = {'data':       path,
               'parameters': parameters,
               'timestamp':  str(datetime.datetime.utcnow()),
               'revision':   revision,
               'system':     sys.version}

    # Save & display results
    with open("results-R4.txt", "w") as fd:
        fd.write(str(results))

    print(path)
\end{code}
\end{minipage}\\

@@

def _rng(seed):
    """ Return a numpy random number generator initialized with seed
        as it would be with python random generator.
    """
    rng = random.Random()
    rng.seed(seed)
    _, keys, _ = rng.getstate()
    rng = np.random.RandomState()
    state = rng.get_state()
    rng.set_state((state[0], keys[:-1], state[2], state[3], state[4]))
    return rng

def walk(n, seed):
    """ Random walk for n steps """

    rng = _rng(seed)
    steps = 2*(rng.uniform(-1,+1,n) > 0) - 1
    return steps.cumsum().tolist()

if __name__ == '__main__':
    # Unit test
    assert walk(n=10, seed=1) == [-1, 0, 1, 0, -1, -2, -1, 0, -1, -2]

    # Random walk for 10 steps, initialization with seed=1
    seed = 1
    path = walk(n=10, seed=seed)

    # Save & display results
    results = {'data': path, 'seed': seed}
    with open("results-R5.txt", "w") as fd:
        fd.write(str(results))
    print(path)

\end{code}
\end{minipage}
